\LARGE{\bf{Natural variation in teosinte at the domestication locus \emph{teosinte branched1} (\emph{tb1})}}\footnotemark

### 2014-05-29 Supplement_mbh.tex
New supplement file added

%Note that if authors wish to submit long DNA sequence appendices as supplemental material, they should select the "DNA sequences (online-only supplemental)" option on Editorial Manager. This ensures that lengthy appendices are not built into the reviewers' PDF, but are still accessible to the reviewers.
\documentclass[11pt]{article}
\usepackage{geometry} 
\usepackage{hyperref}
\usepackage[leftcaption]{sidecap}
\sidecaptionvpos{figure}{c} %position side caption
\usepackage{lineno}
\usepackage{lipsum}
\usepackage{indentfirst}
\usepackage{color}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}  
\usepackage{caption}
\usepackage{natbib}
\usepackage{authblk}
\usepackage[table]{xcolor} %for table line color alteration
\usepackage{subscript}
\usepackage{longtable}
\begin{document}

% Figure S1. Cartoon representation of tb1 locus
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=140mm]{FigS1LocusCartoon.pdf}
   \caption{Representation of the upstream regulatory region of \emph{tb1}, showing the \emph{tb1} coding region (green) and the \emph{Hopscotch} insertion (red). Arrows show the location of primer sets; in black, primers used for amplification and sequencing (Sequenced region 1; within the 5' UTR, and sequenced region 2; 66,169 bp upstream from the tb1 ORF); in blue, primers used to genotype the \emph{Hopscotch} insertion.}
\label{FigS1Locus}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Figure S2. Gel image
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=140mm]{FigS2Gel.png}
   \caption{Agarose gel image of amplification products using our primer sets. Genotypes are indicated at the top of the gel.} 
\label{FigS2Gel}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Figure S3. NJ Trees
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=140mm]{FigS3NJtrees.pdf}
    \caption{Neighbor-Joining tree of the sequenced region in the 5? UTR (right; sequenced region 1) and the 66,169 bp upstream region (left; sequenced region 2) of \emph{tb1}. Individuals with genotype data are colored: Homozygous for the teosinte (no \emph{Hopscotch}) allele (red), homozygous for the maize (\emph{Hopscotch}) allele (blue), heterozygotes (purple). TILs (teosinte inbred lines) are colored in green, with stars indicating the 3 TILs known to have the \emph{Hopscotch} insertion. Black indicates individuals not genotyped for the \emph{Hopscotch} insertion.} 
\label{FigS3NJ}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

@@

    \begin{tabular}{cccc}\\\toprule
    \textbf{Comparison} & \textbf{Region 1} & \textbf{Region 2} & \textbf{\emph{Hopscotch}} \\\midrule
    EjuA \& EjuB & 0     & 0     & 0 \\
    EjuA \& MSA & 0.326 & 0.328 & 0.186 \\
    EjuA \& SLO & 0.416 & 0.258 & 0.280 \\
    EjuB \& MSA & 0.397 & 0.365 & 0.188 \\
    EjuB \& SLO & 0.512  & 0.290 & 0.280 \\
    MSA \& SLO & 0.007  & 0 & 0.016 \\\bottomrule
    \end{tabular}
  \label{Table1Fst}
\end{table}

% Table S2. Parv and mex samples 

@@

\footnotesize  % Switch from 12pt to 11pt; otherwise, table won't fit
\setlength\LTleft{-30pt}            % default: \fill
\setlength\LTright{-30pt}           % default: \fill
\begin{longtable}{llllll}
\caption{Accessions of \emph{Zea mays} ssp. \emph{mexicana} (RIMME) and \emph{Zea mays} ssp. \emph{parviglumis} (RIMPA) sampled. RIHY is a \emph{Z. mays} ssp. 	\emph{parviglumis} and \emph{Zea mays} ssp. \emph{mays} hybrid. } \\
%\hline
\textbf{Accession} & \textbf{USDA ID} & \textbf{Locality} & \textbf{\# Alleles Sampled} & \textbf{\emph{Hopscotch} Frequency} & \textbf{No \emph{Hopscotch} Frequency} \\\toprule
\endhead

@@

    RIMME0014 & 714151 & Breeders line; Puga: 11066 & 6     & 0     & 1 \\

@@

    RIMPA0060 & 714157 & Breeders line: CIMMYT 11355 & 2     & 0     & 1 \\
    RIMPA0061 & 714158 & Breeders line: USDA PI566686 & 4     & 0.5   & 0.5 \\

@@

 \label{TableS1}

@@

\footnotesize  % Switch from 12pt to 11pt; otherwise, table won't fit
\setlength\LTleft{-30pt}            % default: \fill
\setlength\LTright{-30pt}           % default: \fill
\begin{longtable}{lcc}
\caption{\emph{Zea mays} ssp. \emph{mays} (RIMMA) sampled for genotyping} \\
\textbf{Accession} & \textbf{\# Alleles Sampled} & \textbf{\emph{Hopscotch} Frequency} \\\toprule
\endhead

@@

  \label{TableS2Mays}

@@

  \label{TableS3BayEnv}%

@@

% Table S4 Diversity stats in tb1 region based on SNP 50 genotyping data
\begin{table}[htbp]
  \centering
  \caption{Diversity in the \emph{tb1} region based on the maize SNP50 genotyping data}
    \begin{tabular}{ccccc}
    \toprule
    \textbf{Population} & \textbf{\# seg sites} & \textbf{$\theta_{\subscript{\pi}}$ / bp} & \textbf{$\theta_{\subscript{W}}$ / bp} & \textbf{Tajima?s D} \\
    \midrule
    Ejutla A & 4     & 0.15217 & 0.11902 & 0.76191 \\
    Ejutla B & 5     & 0.15258 & 0.14877 & 0.07412 \\
    La Mesa & 3     & 0.12802 & 0.08926 & 1.09209 \\
    San Lorenzo & 3     & 0.09098 & 0.08926 & 0.04845 \\
    \bottomrule
    \end{tabular}%
  \label{TableS4DiversitySNP}%
\end{table}%

\end{document}

>>>>

%Note that if authors wish to submit long DNA sequence appendices as supplemental material, they should select the "DNA sequences (online-only supplemental)" option on Editorial Manager. This ensures that lengthy appendices are not built into the reviewers' PDF, but are still accessible to the reviewers.
\documentclass[11pt]{article}
\usepackage{geometry} 
\usepackage{hyperref}
\usepackage[leftcaption]{sidecap}
\sidecaptionvpos{figure}{c} %position side caption
\usepackage{lineno}
\usepackage{lipsum}
\usepackage{indentfirst}
\usepackage{color}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage{array}
	\newcounter{rowno}
	\setcounter{rowno}{0}
\usepackage{booktabs}
\usepackage[pdftex]{graphicx}  
\usepackage{caption}
\usepackage{natbib}
\usepackage{authblk}
\usepackage[table]{xcolor} %for table line color alteration
\usepackage{subscript}
\usepackage{longtable}

\begin{document}

% Figure S1. Cartoon representation of tb1 locus
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=140mm]{FigS1LocusCartoon.pdf}
   \caption{Representation of the upstream regulatory region of \emph{tb1}, showing the \emph{tb1} coding region (green) and the \emph{Hopscotch} insertion (red). Arrows show the location of primer sets; in black, primers used for amplification and sequencing (Sequenced region 1; within the 5' UTR, and sequenced region 2; 66,169 bp upstream from the tb1 ORF); in blue, primers used to genotype the \emph{Hopscotch} insertion.}
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Figure S2. Gel image
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=100mm]{FigS2Gel.png}
   \caption{Agarose gel image of amplification products using our primer sets. Genotypes are indicated at the top of the gel.} 
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

% Figure S3. NJ Trees
%-------------------------------------------------------------------
\begin{figure*}[!t]
  \begin{center}
   \includegraphics[width=100mm]{FigS3NJtrees.pdf}
    \caption{Neighbor-Joining tree of the sequenced region in the 5? UTR (right; sequenced region 1) and the 66,169 bp upstream region (left; sequenced region 2) of \emph{tb1}. Individuals with genotype data are colored: Homozygous for the teosinte (no \emph{Hopscotch}) allele (red), homozygous for the maize (\emph{Hopscotch}) allele (blue), heterozygotes (purple). TILs (teosinte inbred lines) are colored in green, with stars indicating the 3 TILs known to have the \emph{Hopscotch} insertion. Black indicates individuals not genotyped for the \emph{Hopscotch} insertion.} 
  \end{center}
\end{figure*}
%-------------------------------------------------------------------

@@

    \begin{tabular}{cccc}\\\toprule
    \textbf{Comparison} & \textbf{Region 1} & \textbf{Region 2} & \textbf{\emph{Hopscotch}} \\\midrule
    EjuA \& EjuB & 0     & 0     & 0 \\
    EjuA \& MSA & 0.326 & 0.328 & 0.186 \\
    EjuA \& SLO & 0.416 & 0.258 & 0.280 \\
    EjuB \& MSA & 0.397 & 0.365 & 0.188 \\
    EjuB \& SLO & 0.512  & 0.290 & 0.280 \\
    MSA \& SLO & 0.007  & 0 & 0.016 \\\bottomrule
    \end{tabular}
\end{table}

@@

% Table S2. Parv and mex samples 
\begin{scriptsize}  % Switch from 12pt to 11pt; otherwise, table won't fit
\rowcolors{1}{gray!25}{white}
\begin{longtable}{>{\stepcounter{rowno}}cccccc}
\hiderowcolors
\caption{Accessions of \emph{Zea mays} ssp. \emph{mexicana} (RIMME) and \emph{Zea mays} ssp. \emph{parviglumis} (RIMPA) sampled. RIHY is a \emph{Z. mays} ssp. 	\emph{parviglumis} and \emph{Zea mays} ssp. \emph{mays} hybrid.}\\
\hline
\multicolumn{1}{c}{\textbf{Accession}} & \multicolumn{1}{c}{\textbf{USDA ID}} & \multicolumn{1}{c}{\textbf{Locality}} & \multicolumn{1}{c}{\textbf{Alleles Sampled}} & \multicolumn{1}{c}{\textbf{\emph{Hopscotch} Freq.}} & \multicolumn{1}{c}{\textbf{No \emph{Hopscotch} Freq.}} \\
\hline
\endhead
\showrowcolors

@@

    RIMME0014 & 714151 & Breeders line & 6     & 0     & 1 \\

@@

    RIMPA0060 & 714157 & Breeders line & 2     & 0     & 1 \\
    RIMPA0061 & 714158 & Breeders line & 4     & 0.5   & 0.5 \\

@@

\end{scriptsize}

@@

\tiny
\rowcolors{2}{gray!25}{white}
 \caption{\emph{Zea mays} ssp. \emph{mays} (RIMMA) sampled for genotyping}
    \begin{tabular}{ccc}
 %   \toprule
    Accession & Alleles Sampled & \emph{Hopscotch} Freq. \\
 %   \midrule

@@

    \end{tabular}
\end{table}

@@

@@

% Table S4 Diversity stats in tb1 region based on SNP 50 genotyping data
\begin{table}[htbp]
  \centering
  \caption{Diversity in the \emph{tb1} region based on the maize SNP50 genotyping data}
    \begin{tabular}{ccccc}\\
    \textbf{Population} & \textbf{\# Seg Sites} & \textbf{$\hat\theta_\pi)$ / bp} & \textbf{$\hat\theta_W$ / bp} & \textbf{Tajima's D} \\
    \midrule
    Ejutla A & 4     & 0.15217 & 0.11902 & 0.76191 \\
    Ejutla B & 5     & 0.15258 & 0.14877 & 0.07412 \\
    La Mesa & 3     & 0.12802 & 0.08926 & 1.09209 \\
    San Lorenzo & 3     & 0.09098 & 0.08926 & 0.04845 \\
    \bottomrule
    \end{tabular}%
\end{table}%
\end{document}
